Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-20 Manuscript/sec4-experiments.tex
修改了gaan的一些说明

\paragraph{GaAN}
The top basic operator was \texttt{mm}.
It was used in both the vertex and the edge calculation, where the edge calculation is dominant.
The scalar multiplication \texttt{mul} and the concatenation \texttt{cat} operators were used in the message function $\phi$.

>>>>

\paragraph{GaAN}
The top basic operator was \texttt{addmm}. 
The \texttt{addmm}, the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul} were used in both the vertex and the edge calculation, where the edge calculation is dominant.
